Single-step Hybrid Predition

### 2016-12-06 reports/single_step_kernels.Rmd
Working version of scaled prediction with impute2()

# Kernel Inspection
```{r setup-kernel-inspection, message = FALSE, echo = FALSE}
if (!require("pacman")) install.packages("pacman")
if (!require("devtools")) install.packages("devtools")
devtools::install_github("mwesthues/sspredr", update = TRUE)
pacman::p_load("BGLR","data.table", "parallel", "magrittr", "dplyr", "tidyr",
               "purrr", "testthat", "methods", "tibble", "ggplot2", "stringr",
               "stringi", "lubridate", "readr")
pacman::p_load_gh("mwesthues/sspredr")

>>>>

# Kernel Inspection
```{r setup-kernel-inspection, message = FALSE, echo = FALSE}
if (!require("pacman")) install.packages("pacman")
if (!require("devtools")) install.packages("devtools")
devtools::install_github("mwesthues/sspredr", update = TRUE)
pacman::p_load("BGLR","data.table", "tidyverse", "dtplyr", "caret", "e1071")
pacman::p_load_gh("mwesthues/sspredr")
